---
title: "Chapter03"
output:
  github_document: default
  html_notebook: default
---

## 3. "Analyzing word and document frequency: tf-idf"

A central question in text mining and natural language processing is how to quantify what a document is about. ... The statistic 'tf-idf' is intended to measure how important a word is to a document in a collection (or corpus) of documents


### 3.1 Term frequency in Jane Austen’s novels

Let’s start by looking at the published novels of Jane Austen and examine first term frequency, then tf-idf.
```{r}
library(dplyr)
library(janeaustenr)
library(tidytext)

book_words <- austen_books() %>%          # most commonly used words in Jane Austen’s novels
  unnest_tokens(word, text) %>%
  count(book, word, sort = TRUE) %>%
  ungroup()                               # cols : book, word, n

total_words <- book_words %>%             # total words in each novel, for later use
  group_by(book) %>% 
  summarize(total = sum(n))

book_words <- left_join(book_words, total_words)          # cols : book, word, n, total
```


let’s look at the distribution of n/total for each novel ... This is exactly what term frequency is.
```{r}
library(ggplot2)

ggplot(book_words, aes(n/total, fill = book)) +
  geom_histogram(show.legend = FALSE) +
  xlim(NA, 0.0009) +
  facet_wrap(~book, ncol = 2, scales = "free_y")
```

...There are very long tails to the right for these novels (those extremely common words!) that we have not shown in these plots



### 3.2 Zipf’s law

Zipf’s law states that the frequency that a word appears is inversely proportional to its rank.
```{r}
freq_by_rank <- book_words %>% 
  group_by(book) %>% 
  mutate(rank = row_number(), `term frequency` = n/total)
```


Zipf’s law is often visualized by plotting rank on the x-axis and term frequency on the y-axis, on logarithmic scales. Plotting this way, an inversely proportional relationship will have a constant, negative slope.
```{r}
freq_by_rank %>% 
  ggplot(aes(rank, `term frequency`, color = book)) + 
  geom_abline(intercept = -0.62, slope = -1.1, color = "gray50", linetype = 2) +    # by lin/regression
  geom_line(size = 1.1, alpha = 0.8, show.legend = FALSE) + 
  scale_x_log10() +
  scale_y_log10()
```

...The deviations we see here at high rank are not uncommon ... The deviations at low rank are more unusual.



### 3.3 The `bind_tf_idf` function
### 3.4 A corpus of physics texts
### 3.5 Summary

